---
title: "Model Performance - Logistic Regression"
author: "Rajanish Rajagopalan"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Initial Analysis 

```{r echo=FALSE, message=FALSE}
data <- myUtils::load_data_raw()
train_data <- data[[1]]
test_data <- data[[2]]
features <- names(train_data)[!names(train_data) %in% "y"]
x1 <- toString(length(which(data[[1]][['y']]=='yes')) + length(which(data[[2]][['y']]=='yes')))
y1 <- x1
y1x1 <- '100%'
x <- toString(nrow(data[[1]]) + nrow(data[[2]]))
y <- x1
yx <- paste(toString(as.integer(y)/as.integer(x)*100),'%')
```

The marketing team took the customer sales leads and conducted a survey to determine the actual number of customers interested in buying bank products. The marketing team collected these customer attributes (`r toString(features)`).

A total of **`r x` (X)** customers participated in the Marketing team research of whom **`r y` (Y)** were interested in buying. The objective project is to get **X$^{1}$** closest to **Y** i.e. a full success rate.

```{r Initial_Analysis, echo = FALSE, results='asis'}
library(knitr,stringr)
table <- data.frame('CurrentProcess' = c(stringr::str_c('Sales leads X: ', x),stringr::str_c('Products Sold Y: ', y)
                                    ,stringr::str_c('Success Rate (Y/X): ', yx)), 
                    'IdealProcess' = c(stringr::str_c('Sales leads X$^{1}$: ',x1),stringr::str_c('Products Sold Y$^{1}$: ', y1)
                                    ,stringr::str_c('Success Rate (Y$^{1}$/X$^{1}$): ',y1x1)))
kable(table,caption = 'Measuring Success: Ideal Scenario')
```


## Model Performance
As an initial step, we will build a simple Linear classifier and evaluate Model performance. 

Splitting the available data into **training (`r nrow(train_data)` at 80%)** and **testing (`r nrow(test_data)` at 20%)** data sets.

```{r Model_Performance, echo = FALSE, results='asis'}
library(knitr,stringr)
library(pkgGLM)
confusion <- pkgGLM:::score()
x1 <- toString(length(data[[2]][['y']]))
y1 <- toString(length(which(data[[2]][['y']]=='yes')))
y1x1 <- paste(toString(as.integer(y1)/as.integer(x1)*100),'%')
x2 <- toString(confusion[2,2] + confusion[1,2])
y2 <- toString(confusion[2,2])
y2x2 <- paste(toString(confusion[2,2]/(confusion[2,2] + confusion[1,2])*100),'%')
table <- data.frame('CurrentProcess' = c(stringr::str_c('Sales leads X: ', x1),stringr::str_c('Products Sold Y: ', y1)
                                    ,stringr::str_c('Success Rate (Y/X): ', y1x1)), 
                    'FutureProcess' = c(stringr::str_c('Sales leads X$^{1}$: ',x2),stringr::str_c('Products Sold Y$^{1}$: ', y2)
                                    ,stringr::str_c('Success Rate (Y$^{1}$/X$^{1}$): ',y2x2)))
kable(table,caption = 'Measuring Success: Baseline')
```

Using the standard Confusion matrix to evalute the model performance.
```{r Confusion, echo = FALSE, results='asis'}
library(knitr,stringr)

kable(confusion,caption = 'Confusion Matrix: Baseline')
```

## Conclusion
Even though the Sales effort reduced and the success rate is higher, we are losing a lot of potential customers. We will have to significantly improve the performance.
